---
title: "Quantify Relationship between Brain Patterns and Symptoms of Schizophrenia "
subtitle: "UCLA Stats 141SL Project Codes"
author: "Xiaojing Zhu, Haorui Zhang, Chen Wen, Xinyan Li, Yufei Den"
date: "3/20/2018"
output: pdf_document
---

```{r message = FALSE}
library(car)
library(dplyr)
library(readxl)
library(ggplot2)
library(stringr)
library(data.table)
library(randomForestSRC)
```

# 1. Data Cleaning

```{r warning = FALSE}
# Load the data
COBRE_between_nets <- read.csv("~/Desktop/Group9/COBRE_between_nets.txt", sep="")
COBRE_within_nets <- read.csv("~/Desktop/Group9/COBRE_within_nets.txt", sep="")
CNP_between_nets <- read.csv("~/Desktop/Group9/CNP_between_nets.txt", sep="")
CNP_within_nets <- read.csv("~/Desktop/Group9/CNP_within_nets.txt", sep="")
CNP_SANS_SAPS_BPRS <- read_excel("~/Desktop/Group9/CNP_SANS_SAPS_BPRS.xls", sheet = "Sheet1")
PANSS <- read_excel("~/Desktop/Group9/COBRE INDI Additional data.xls", sheet = "PANSS")
```

## 1.1 Data Preparation for COBRE
```{r}
# Merge the three data sets from the COBRE study
# Extract ID
COBRE_within_nets$Subject_ID <- as.character(COBRE_within_nets$Subject_ID)
COBRE_between_nets$Subject_ID <- as.character(COBRE_between_nets$Subject_ID)

numextract <- function(string){ 
  str_extract(string, "\\d+\\.*\\d*")
} 

COBRE_within_nets$ID <- as.character(numextract(COBRE_within_nets$Subject_ID))
COBRE_between_nets$ID <- as.character(numextract(COBRE_between_nets$Subject_ID))

# Create a new data COBRE after merging between nets, within nets, and PANSS by ID
COBRE <- merge(COBRE_within_nets,PANSS, by = "ID")
COBRE <- merge(COBRE_between_nets, COBRE, by = "ID")
```

```{r}
# Sum up 5 dimensions of PANSS
COBRE$Uncooperativeness <- as.numeric(COBRE$Uncooperativeness) # one "MD" (missing data) is coerced to NA

COBRE$Negative <- COBRE$`Blunted Affect` + COBRE$`Emotional Withdrawal` + COBRE$`Poor Rapport` + COBRE$`Passive/Apathetic Social Withdrawal` + COBRE$`Lack of Spontaneity and Flow of Conversation` + COBRE$`Motor Retardation` + COBRE$`Active Social Avoidance` + COBRE$`Disturbance of Volition`

COBRE$Positive<- COBRE$Delusions + COBRE$`Hallucinatory Behavior` + COBRE$Grandiosity + COBRE$`Suspiciousness/Persecution` + COBRE$`Stereotyped Thinking` + COBRE$`Somatic Concern`+COBRE$`Unusual Thought Content`+ COBRE$Preoccupation

COBRE$Disorganized <- COBRE$`Stereotyped Thinking` + COBRE$`Lack of Judgment and Insight` + COBRE$`Conceptual Disorganization` + COBRE$`Difficulty in Abstract Thinking` + COBRE$`Mannerisms and Posturing` + COBRE$`Poor Attention` + COBRE$`Disturbance of Volition` + COBRE$Preoccupation + COBRE$Disorientation

COBRE$Excited <- COBRE$Excitement + COBRE$Hostility + as.numeric(COBRE$Uncooperativeness) + COBRE$`Poor Impulse Control`

COBRE$Anxiety <- COBRE$Anxiety + COBRE$`Guilt Feelings` + COBRE$Tension+COBRE$Depression + COBRE$`Somatic Concern`
```

```{r}
sum(is.na(COBRE))
COBRE <- na.omit(COBRE)
COBRE <- COBRE[, -c(2, 97:100, 171:186, 188:201)]

# Subset COBRE to explore between and within measurements
COBRE_between <- COBRE[ ,c(5:95, 166:170)]
COBRE_within <- COBRE[ ,c(96:170)]

# Export clean COBRE data
write.csv(COBRE, file = "~/Desktop/Group9/COBRE.csv")
```

```{r}
# Clean the CORBRE Medication Data
# Import the medication data set from the COBRE study
Med <- read_excel("~/Desktop/Group9/COBRE INDI Additional data.xls", sheet = "COBRE INDI Medication Log")
Med <- Med[ , -1]

# Transpose the data
Med <- t(Med)
colnames(Med) <- Med[1, ]

# Subset medications
Med <- Med[ , c(1, 11, 20, 30, 40)]
Med <- data.frame(Med[-1, ])

# Create a new column ID from the rownames
Med <- setDT(Med, keep.rownames = TRUE)[]
ID_label <- na.omit(melt(Med, id="rn"))
ID_label <- ID_label[ , -2]
colnames(ID_label) <- c("ID","Label")
ID_label$ID <- as.integer(ID_label$ID)

# Import names of medication
name <- read_excel("~/Desktop/Group9/COBRE INDI Additional data.xls", sheet = "Med. Codes")
colnames(name) <- c("Label", "name")

# Now we have patient ID ane the name of medication s/he takes
ID_name <- merge(name, ID_label, by = "Label")
```

```{r}
# We research on whether the medication is a 1st generation or 2nd geneartion antipsychotic drugs, and create a new excel file containing this information
COBRE_Med <- read_excel("~/Desktop/Group9/Question 2.xlsx", sheet = "Q2")
COBRE$ID <- as.integer(COBRE$ID)
COBRE_Med <- merge(COBRE_Med, COBRE, by = "ID")
COBRE_Med <- COBRE_Med[ ,c(1:3, 98:111, 168:172)]

# Creating a new variable "Medication", which contains information about whether the patient takes 1st generation medication (1.0), 2nd generation medication (0.1), or both (1.1)
COBRE_Med$Medication <- with(COBRE_Med, interaction(`Generation 1`,  `Generation 2`))
levels(COBRE_Med$Medication)

# Remove (0.0)
COBRE_Med$Medication <- factor(COBRE_Med$Medication)
levels(COBRE_Med$Medication)

write.csv(COBRE_Med, file = "~/Desktop/Group9/COBRE_Med.csv")
```


## 1.2 Data Preparation for CNP

```{r}
# Merging the three data sets from the CNP study
# Extract ID
CNP_within_nets$Subject_ID <- as.character(CNP_within_nets$Subject_ID)
CNP_between_nets$Subject_ID <- as.character(CNP_between_nets$Subject_ID)

numextract <- function(string){ 
  str_extract(string, "\\d+\\.*\\d*")
} 

CNP_within_nets$PTID <- as.character(numextract(CNP_within_nets$Subject_ID))
CNP_between_nets$PTID <- as.character(numextract(CNP_between_nets$Subject_ID))

# Create a new data CNP after merging between nets, within nets, and SANS/SAPS by ID
CNP <- merge(CNP_within_nets,CNP_SANS_SAPS_BPRS, by = "PTID")
CNP <- merge(CNP_between_nets, CNP, by = "PTID")

# Filter out schizophrenia patients only
CNP <- filter(CNP, Subject_Type.x == "Schizophrenia")
```

```{r}
# Convert SANS/SAPS to numeric
num <- c(173:196, 209:243)
for(i in num) {
  CNP[ ,i] <- as.numeric(CNP[ ,i])
}
```

```{r}
# Remove unuseful columns
CNP <- CNP[ , - c(171, 172, 197:208, 244:294)]

# Create new variables containing sum of SANS and SAPS scores
CNP$SANS_sum <- rowSums(CNP[ ,171:194])
CNP$SAPS_sum <- rowSums(CNP[ ,195:229])
```

```{r}
sum(is.na(CNP))
CNP <- CNP[, -c(2, 97:100, 171:229)]

# Subset CNP to explore between and within measurements
CNP_between <- CNP[ ,c(5:95, 166:167)]
CNP_within <- CNP[ ,c(96:165, 166:167)]

# Export clean CNP data
write.csv(CNP, file = "~/Desktop/Group9/CNP.csv")
```

# 2. Data Exploration

## 2.1.1 Data Exploration for COBRE

```{r}
# COBRE study has 91 predictors between networks, 70 predictors within networks, and 69 observations
dim(COBRE) 
# Outcome variable is 5-dimensional
summary(COBRE$Negative)
summary(COBRE$Positive)
summary(COBRE$Disorganized)
summary(COBRE$Excited)
summary(COBRE$Anxiety)
```

```{r  echo=FALSE}
# Histograms for the 5 dimensions of PANSS
barfill <- "#4271AE"
barlines <- "#1F3552"

ggplot(COBRE, aes(x = Negative)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Negative Symptons of PANSS",
                           breaks = seq(0, 35, 1),
                           limits=c(0, 35)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 10, 1), limits = c(0, 10)) +
        ggtitle("Histogram of Negative Symptons of PANSS") +
        theme_bw() +
        theme(axis.line = element_line(size = 1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
              plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))


ggplot(COBRE, aes(x = Positive)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Positive Symptons of PANSS",
                           breaks = seq(0, 40, 1),
                           limits=c(0, 40)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 10, 1), limits = c(0, 10)) +
        ggtitle("Histogram of Positive Symptons of PANSS") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
              plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))


ggplot(COBRE, aes(x = Disorganized)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Disorganized Symptons of PANSS",
                           breaks = seq(0, 30, 1),
                           limits=c(0, 30)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 10, 1), limits = c(0, 10)) + 
        ggtitle("Histogram of Disorganized Symptons of PANSS") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
              plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))


ggplot(COBRE, aes(x = Excited)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Excited Symptons of PANSS",
                           breaks = seq(0, 20, 1),
                           limits=c(0, 20)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 40, 5), limits = c(0, 40))+
        ggtitle("Histogram of Excited Symptons of PANSS") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
            plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))


ggplot(COBRE, aes(x = Anxiety)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Anxiety Symptons of PANSS",
                           breaks = seq(0, 50, 1),
                           limits=c(0, 50)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 10, 1), limits = c(0, 10)) + 
        ggtitle("Histogram of Anxiety Symptons of PANSS") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
              plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 5),
              axis.text.y=element_text(colour="black", size = 9))
```

```{r}
# COBRE Preditors only
COBRE_between_p <- COBRE[ ,c(5:95)]
COBRE_within_p <- COBRE[ ,c(96:165)]

min(COBRE_between_p)
max(COBRE_between_p)

min(COBRE_within_p)
max(COBRE_within_p) #outlier

which.max(apply(COBRE_within_p, MARGIN=2, max)) # Memory_retrieval.char_path_length, not included in the model
max(COBRE_within_p[COBRE_within_p != max(COBRE_within_p)]) #6.69197
which(COBRE_within_p == 6.69197)
colnames(COBRE_within_p)[which(COBRE_within_p == 6.69197, arr.ind = TRUE)[2]] #"Uncertain.char_path_length", not included
```

```{r}
# cor(COBRE_between) shows large (>0.4) correlation coefficients
# cor(COBRE_within) shows large (>0.4) correlation coefficients

# Correlation between the brain pattern measurements (the predictors) and the 5 dimensions of PANSS

# COBRE measures vs. Negative Symptoms in PANSS
BN <- round(cor(COBRE_between_p, COBRE$Negative), 3)
WN <- round(cor(COBRE_within_p, COBRE$Negative), 3)

# COBRE measures vs. Positive Symptoms in PANSS
BP <- round(cor(COBRE_between_p, COBRE$Positive), 3)
WP <- round(cor(COBRE_within_p, COBRE$Positive), 3)

# COBRE measures vs. Disorganized Symptoms in PANSS
BD <- round(cor(COBRE_between_p, COBRE$Disorganized), 3)
WD <- round(cor(COBRE_within_p, COBRE$Disorganized), 3)

# COBRE measures vs. Excited Symptoms in PANSS
BE <- round(cor(COBRE_between_p, COBRE$Excited), 3)
WE <- round(cor(COBRE_within_p, COBRE$Excited), 3)

# COBRE measures vs. Anxiety Symptoms in PANSS
BA <- round(cor(COBRE_between_p, COBRE$Anxiety), 3)
WA <- round(cor(COBRE_within_p, COBRE$Anxiety), 3)
```

```{r}
summary(BN)
summary(BP)
summary(BD)
summary(BE)
summary(BA)

mean(abs(BN))
mean(abs(BP))
mean(abs(BD))
mean(abs(BE))
mean(abs(BA))

summary(WN)
summary(WP)
summary(WD)
summary(WE)
summary(WA)

mean(abs(WN))
mean(abs(WP))
mean(abs(WD))
mean(abs(WE))
mean(abs(WA))
```


## 2.1.2 Data Exploration for COBRE_Med
```{r}
# dim
dim(COBRE_Med)

# Max and Min of 14 Small World fMRI measurements
min(COBRE_Med[ ,4:17])
max(COBRE_Med[ ,4:17])

colMeans(COBRE_Med[ ,4:17])

# Table of Medication Types
table(COBRE_Med$Medication)
```


## 2.2 Data Exploration for CNP

```{r}
# CNP study has 91 predictors between networks, 70 predictors within networks, and 42 observations
dim(CNP)
# Outcome variable is 2-dimensional
summary(CNP$SANS_sum)
summary(CNP$SAPS_sum)
```


```{r echo=FALSE}
# Histograms to visualize the distribution of "SANS_sum" and "SAPS"
barfill <- "#8f86ef"
barlines <- "#1F3552"

ggplot(CNP, aes(x = SANS_sum)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Sum of SANS Scores",
                           breaks = seq(0, 30, 1),
                           limits=c(0, 30)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 7, 1), limits = c(0, 7)) +
        ggtitle("Histogram of SANS Scores") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
              plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))

ggplot(CNP, aes(x = SAPS_sum)) +
        geom_histogram(aes(y = ..count..), binwidth = 1,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Sum of SAPS Scores",
                           breaks = seq(0, 30, 1),
                           limits=c(0, 30)) +
        scale_y_continuous(name = "Count", breaks = seq(0, 7, 1), limits = c(0, 7)) +
        ggtitle("Histogram of SAPS Scores") +
        theme_bw() +
        theme(axis.line = element_line(size=1, colour = "black"),
              panel.grid.major = element_line(colour = "#d3d3d3"),
              panel.grid.minor = element_blank(),
              panel.border = element_blank(), panel.background = element_blank(),
             plot.title = element_text(size = 14, face = "bold"),
              axis.text.x=element_text(colour="black", size = 7),
              axis.text.y=element_text(colour="black", size = 9))
```

```{r}
# CNP Preditors only
CNP_between_p <- CNP[ ,c(5:95)]
CNP_within_p <- CNP[ ,c(96:165)]

min(CNP_between_p)
max(CNP_between_p)

min(CNP_within_p)
max(CNP_within_p)

which.max(apply(CNP_within_p, MARGIN=2, max)) #Cerebellar.char_path_length
```

```{r}
#CNP measures vs. SANS
# cor(CNP_between) shows large (>0.4) correlation coefficients
# cor(CNP_within) shows large (>0.4) correlation coefficients

# Correlation between the brain pattern measurements (the predictors) and the SANS_sum and SAPS_sum (the outcomes)
BSANS <- round(cor(CNP_between_p, CNP$SANS_sum), 3)
WSANS <- round(cor(CNP_within_p, CNP$SANS_sum), 3)

#CNP measures vs. SAPS
BSAPS <- round(cor(CNP_between_p, CNP$SAPS_sum), 3)
WSAPS <- round(cor(CNP_within_p, CNP$SAPS_sum), 3)
```

```{r}
summary(BSANS)
summary(BSAPS)
summary(WSANS)
summary(WSAPS)

mean(abs(BSANS))
mean(abs(BSAPS))
mean(abs(WSANS))
mean(abs(WSAPS))
```


# 3. Models

## 3.1 Question 1: *Are brain patterns related to symptoms? Do fMRI patterns map to the PANSS symptoms in COBRE, and SANS/SAPS in CNP?*

### 3.1.1 Random Forest Feature Selection

```{r}
COBRE_B <- rfsrc(Multivar(Negative, Positive, Disorganized, Excited, Anxiety) ~., data = COBRE_between, importance = TRUE)
var.select(COBRE_B, method = "vh.vimp")
```

```{r}
COBRE_W <- rfsrc(Multivar(Negative, Positive, Disorganized, Excited, Anxiety) ~., data = COBRE_within, importance = TRUE)
var.select(COBRE_W, method = "vh.vimp")
```

```{r}
CNP_B <- rfsrc(Multivar(SANS_sum, SAPS_sum) ~., data = CNP_between, importance = TRUE)
var.select(CNP_B, method = "vh.vimp")
```

```{r}
CNP_W <- rfsrc(Multivar(SANS_sum, SAPS_sum) ~., data = CNP_within, importance = TRUE)
var.select(CNP_W, method = "vh.vimp")
```

### 3.1.2 Multivariate Models
```{r}
# COBRE Multivariate Model
COBRE_m1 <- lm(cbind(Negative, Positive, Disorganized, Excited, Anxiety) ~ Sensory.Hand..Fronto.parietal + Visual.Auditory + Visual.Sensory.Hand. + Salience.Dorsal_Attention + Sensory.Mouth..Fronto.parietal + Sensory.Mouth..Auditory + Salience.Auditory + Sensory.Hand..Dorsal_Attention + Sensory.Mouth..Dorsal_Attention + Visual.Dorsal_Attention + Sensory.somatomotor_Hand.small_world + Sensory.somatomotor_Hand.char_path_length + Dorsal_attention.clust_coef + Cingulo.opercular_Task_Control.global_eff, data = COBRE)

summary(COBRE_m1)
Manova(COBRE_m1)
```

```{r}
# CNP Multivariate Model
CNP_m1 <- lm(cbind(SANS_sum,SAPS_sum) ~ Sensory.Hand..Default_Mode + Default_Mode.Auditory + Fronto.parietal.Cerebellar + Visual.Cerebellar + Uncertain.Default_Mode + Salience.Cerebellar + Default_Mode.Cerebellar+ Dorsal_attention.small_world + Sensory.somatomotor_Hand.small_world + Sensory.somatomotor_Hand.global_eff+ Auditory.mod, data = CNP)

summary(CNP_m1)
Manova(CNP_m1)
```

### 3.1.3 Cross Study Prediction
```{r}
# Scale the COBRE and CNP data so that we can perform cross study validation 
COBRE_scale <- COBRE
COBRE_scale$Negative <- scale(COBRE_scale$Negative)
COBRE_scale$Positive <- scale(COBRE_scale$Positive)
COBRE_scale$Disorganized <- scale(COBRE_scale$Disorganized)
COBRE_scale$Excited <- scale(COBRE_scale$Excited)
COBRE_scale$Anxiety <- scale(COBRE_scale$Anxiety)

# all means = 0
colMeans(COBRE_scale$Negative) 
colMeans(COBRE_scale$Positive)
colMeans(COBRE_scale$Disorganized)
colMeans(COBRE_scale$Excited)
colMeans(COBRE_scale$Anxiety)

# all sd = 1
apply(COBRE_scale$Negative, 2, sd) 
apply(COBRE_scale$Positive, 2, sd)
apply(COBRE_scale$Disorganized, 2, sd)
apply(COBRE_scale$Excited, 2, sd)
apply(COBRE_scale$Anxiety, 2, sd)

CNP_scale <- CNP
CNP_scale$SANS_sum <- scale(CNP_scale$SANS_sum)
CNP_scale$SAPS_sum <- scale(CNP_scale$SAPS_sum)

# all means = 0
colMeans(CNP_scale$SANS_sum) 
colMeans(CNP_scale$SAPS_sum)

 # all sd = 1
apply(CNP_scale$SANS_sum, 2, sd)  
apply(CNP_scale$SAPS_sum, 2, sd)
```

```{r}
# This is our best model based on the COBRE data (using the scaled data)
COBRE_s <- lm(formula = cbind(Negative, Positive, Disorganized, Excited, Anxiety) ~ Sensory.Hand..Fronto.parietal + Visual.Auditory + Visual.Sensory.Hand. + Salience.Dorsal_Attention + Sensory.Mouth..Fronto.parietal + Sensory.Mouth..Auditory + Salience.Auditory + Sensory.Hand..Dorsal_Attention + Sensory.Mouth..Dorsal_Attention + Visual.Dorsal_Attention + Sensory.somatomotor_Hand.small_world + Sensory.somatomotor_Hand.char_path_length + Dorsal_attention.clust_coef + Cingulo.opercular_Task_Control.global_eff, data = COBRE_scale)

summary(COBRE_s)
```

```{r}
# Cross Study Validation
# Using the COBRE model to predicting SANS (positive syndromes) and SAPS (negative syndromes) based on CNP testing data
CNP_test <- CNP[ ,c(5:165)]
cross_pred <- as.data.frame(predict(COBRE_s, data.frame(CNP_test)))
colnames(cross_pred) <- c("Negative", "Positive", "Disorganized", "Excited", "Anxiety")

# Negative syndromes
SSR_n <- sum((cross_pred$Negative - mean(CNP_scale$SANS_sum))^2)
SST_n <- sum((CNP_scale$SANS_sum - mean(CNP_scale$SANS_sum))^2)
SSR_n/SST_n # Gives us an R-square of 0.4007224

# Positive syndromes
SSR_p <- sum((cross_pred$Positive - mean(CNP_scale$SAPS_sum))^2)
SST_p <- sum((CNP_scale$SAPS_sum - mean(CNP_scale$SAPS_sum))^2)
SSR_p/SST_p # Gives us an R-square of 0.5442006
```

## 3.2 Question 2: *Are symptoms and brain markers associated with medications (in the COBRE study)?*

Perhaps a better model would be to see whether there is an interaction between fMRI and medication in predicting symptoms:
PANSS_POSITIVE = (fMRI Measures) * Medications (as factors A, B, AB)
Perhaps just use the within nets measures- small world to reduce the variables.


```{r}
# Q2 <- lm(cbind(Negative, Positive, Disorganized, Excited, Anxiety) ~ Medication * Auditory.small_world + Medication * Cerebellar.small_world + Medication * Cingulo.opercular_Task_Control.small_world + Medication * Default_mode.small_world + Medication * Dorsal_attention.small_world + Medication * Fronto.parietal_Task_Control.small_world + Medication *  Memory_retrieval.small_world + Medication * Salience.small_world + Medication * Sensory.somatomotor_Hand.small_world + Medication * Sensory.somatomotor_Mouth.small_world + Medication * Subcortical.small_world + Medication * Uncertain.small_world + Medication * Ventral_attention.small_world + Medication * Visual.small_world , data = COBRE_Med)
# summary(Q2)
# alias(Q2)
```

```{r}
# Drop (1.0) (3 observations that has high collinearity)
COBRE_Med_model <- COBRE_Med[COBRE_Med$Medication != "1.0", ]

# Multivariate Model for Question 2
Q2_m <- lm(cbind(Negative, Positive, Disorganized, Excited, Anxiety) ~ Medication * Auditory.small_world + Medication * Cerebellar.small_world + Medication * Cingulo.opercular_Task_Control.small_world + Medication * Default_mode.small_world + Medication * Dorsal_attention.small_world + Medication * Fronto.parietal_Task_Control.small_world + Medication *  Memory_retrieval.small_world + Medication * Salience.small_world + Medication * Sensory.somatomotor_Hand.small_world + Medication * Sensory.somatomotor_Mouth.small_world + Medication * Subcortical.small_world + Medication * Uncertain.small_world + Medication * Ventral_attention.small_world + Medication * Visual.small_world , data = COBRE_Med_model)

summary(Q2_m)

Manova(Q2_m)
```

```{r}
# Interaction plots for significant interaction effects
# Negative PANSS: None of the interactions between fMRI and medication type is significant

# Positive PANSS
COBRE_Med %>%
ggplot() +
  aes(x = Auditory.small_world, color = Medication, group = Medication, y = Positive) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Positive PANSS") +
  xlab("Auditory Small World (fMRI)") + ylab("Positive PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Fronto.parietal_Task_Control.small_world, color = Medication, group = Medication, y = Positive) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Positive PANSS") +
  xlab("Fronto Parietal Task Control World (fMRI)") + ylab("Positive PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Memory_retrieval.small_world, color = Medication, group = Medication, y = Positive) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Positive PANSS") +
  xlab("Memory Retrieval Small World (fMRI)") + ylab("Positive PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Salience.small_world, color = Medication, group = Medication, y = Positive) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Positive PANSS") +
  xlab("Salience Small World (fMRI)") + ylab("Positive PANSS")
```

```{r}
# Interaction plots for significant interaction effects
# Disorganized PANSS
COBRE_Med %>%
ggplot() +
  aes(x = Auditory.small_world, color = Medication, group = Medication, y = Disorganized) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Disorganized PANSS") +
  xlab("Auditory Small World (fMRI)") + ylab("suDisorganized PANSS")
```

```{r}
# Interaction plots for significant interaction effects
# Excited PANSS
COBRE_Med %>%
ggplot() +
  aes(x = Salience.small_world, color = Medication, group = Medication, y = Excited) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Excited PANSS") +
  xlab("Salience Small World (fMRI)") + ylab("Excited PANSS")
```

```{r}
# Interaction plots for significant interaction effects
# Anxiety PANSS
COBRE_Med %>%
ggplot() +
  aes(x = Auditory.small_world, color = Medication, group = Medication, y = Anxiety) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Anxiety PANSS") +
  xlab("Auditory Small World (fMRI)") + ylab("Anxiety PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Fronto.parietal_Task_Control.small_world, color = Medication, group = Medication, y = Anxiety) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Anxiety PANSS") +
  xlab("Fronto Parietal Task Control World (fMRI)") + ylab("Anxiety PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Salience.small_world, color = Medication, group = Medication, y = Anxiety) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Anxiety PANSS") +
  xlab("Salience Small World (fMRI)") + ylab("Anxiety PANSS")

COBRE_Med %>%
ggplot() +
  aes(x = Uncertain.small_world, color = Medication, group = Medication, y = Anxiety) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")  + 
  theme_bw() + scale_color_manual(values=c("#ffcc66", "#4da6ff", "#ff6699")) + 
  ggtitle("Significant Interaction Between Medication Type and fMRI for Anxiety PANSS") +
  xlab("Uncertainty Small World (fMRI)") + ylab("Anxiety PANSS")
```
